SULI Report!

### 2015-08-19 doc/suli-report-swe.tex
Fixed calls to make the References section, changed it to a single column format. #81

Instead of comparing the ray-traced and \texttt{Pangloss}-predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A. Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition\cite{schneider}, see Appendix B.

@@

@@

%\bibliographystyle{plain}
%\bibliography{suli-report-swe}

\onecolumngrid
\section{Appendix}

@@

% Bibliography

>>>>

Instead of comparing the ray-traced and \texttt{Pangloss}-predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see Appendix A. Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publically available \texttt{TreeCorr} module written by Mike Jarvis (website url?). Note that the correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition\cite{schneider}, see Appendix B.

@@

\onecolumngrid

@@

\bibliographystyle{plain}
\bibliography{suli-report-swe}

\section{Appendix}

@@
